Manual classification of tumor cells

### 2024-07-10 analyses/cell-type-ewings/template_notebooks/cnv-workflow/01-marker-genes.Rmd
test changing criterion for find root

```{r base paths}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::is_git_root)

>>>>

```{r base paths}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::has_file("LICENSE.md"))
